Self Regulation Ontology Retest Analyses

### 2018-10-16 code/SRO_Retest_Analyses.Rmd
refactoring

Post process dv's from cluster to calculate reliabilities
```{r}
t1_dvs = t1_dvs %>% select(-X)
t2_dvs = t2_dvs %>% select(-X)
```

```{r eval=FALSE}
hr_merge = merge(t1_dvs, t2_dvs, by = c("worker_id", "level_1"))

hr_merge = hr_merge %>%
  gather(key, value, -worker_id, -level_1) %>%
  separate(key, c("dv", "time"), sep="\\.") %>%
  mutate(time = ifelse(time == "x", 1, 2))%>%
  rename(sub_id = worker_id,
         breaks = level_1)

t1_dvs = hr_merge %>%
  filter(time == 1) %>%
  select(-time) %>%
  spread(dv, value)

t2_dvs = hr_merge %>%
  filter(time == 2) %>%
  select(-time) %>%
  spread(dv, value)

# calculate point estimates for reliability of each of the variables for each break
# get_icc for each break of tmp_t1_dvs and tmp_t2_dvs

trial_num_rel_df = data.frame(breaks=rep(NA, length(unique(t1_dvs$breaks))),
                              acc_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              avg_rt_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              conceptual_responses_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              fail_to_maintain_set_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              learning_rate_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              learning_to_learn_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              nonperseverative_errors_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              perseverative_errors_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              perseverative_responses_icc=rep(NA, length(unique(t1_dvs$breaks))),
                              total_errors_icc=rep(NA, length(unique(t1_dvs$breaks))))

for(i in 1:length(unique(t1_dvs$breaks))){
  cur_break = unique(t1_dvs$breaks)[i]
  tmp_t1_dvs = t1_dvs %>% filter(breaks == cur_break)
  tmp_t2_dvs = t2_dvs %>% filter(breaks == cur_break)
  trial_num_rel_df$breaks[i] = cur_break
  trial_num_rel_df$acc_icc[i] = get_icc("acc", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$avg_rt_icc[i] = get_icc("avg_rt", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$conceptual_responses_icc[i] = get_icc("conceptual_responses", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$fail_to_maintain_set_icc[i] = get_icc("fail_to_maintain_set", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$learning_rate_icc[i] = get_icc("learning_rate", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$learning_to_learn_icc[i] = get_icc("learning_to_learn", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$nonperseverative_errors_icc[i] = get_icc("nonperseverative_errors", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$perseverative_errors_icc[i] = get_icc("perseverative_errors", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$perseverative_responses_icc[i] = get_icc("perseverative_responses", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$total_errors_icc[i] = get_icc("total_errors", tmp_t1_dvs, tmp_t2_dvs)
}
rm(i, cur_break, tmp_t1_dvs, tmp_t2_dvs)

trial_num_rel_df$breaks = as.numeric(trial_num_rel_df$breaks)

# write.csv(trial_num_rel_df, paste0(retest_data_path, 'trial_num_rel_df_shift.csv'))
```

@@

```{r warning=FALSE, message=FALSE}
trial_num_rel_df %>%
  gather(key, value, -breaks) %>%
  filter(key %in% c("avg_rt_icc", "learning_to_learn_icc", "nonperseverative_errors_icc")) %>%
  ggplot(aes((breaks+1)*10, value, shape=key))+
  geom_point()+
  geom_line(alpha = 0.5)+
  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
                             plot.caption = element_text(family = "Times", lineheight = 2, hjust = 0)) +
  scale_shape_manual(values = c(0:9),
                     breaks = c("avg_rt_icc","learning_to_learn_icc", "nonperseverative_errors_icc"),
                     labels = c("Average Response Time", "Learning to Learn",  "Nonperseverative Errors")) +
  labs(caption = str_wrap("FIGURE 6: Change in point estimates of ICC for three dependent measures selected from the Shift task using increasing numbers of trials to estimate them. These measures show the different types of relationships reliability estimates have based on the trial numbers used to estimate them.", width = 180))

ggsave('Shift_Task_Intrameasure_Trialnum_Dependendence.tiff', device = "tiff", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 5, units = "in", dpi = 300)
```

@@

```{r}
# summary(lmerTest::lmer(icc ~ contrast + (1|dv) ,tmp))
summary(MCMCglmm(icc ~ contrast, random = ~ dv, data=tmp))
```

@@

```{r}
ddm_boot_plot = tmp %>%
  group_by(dv) %>%
  summarise(mean_icc = mean(icc),
            raw_fit = unique(raw_fit),
            contrast = unique(contrast),
            rt_acc = unique(rt_acc)) %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), mean_icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_wrap(~factor(contrast, levels=c("non-contrast", "contrast"), labels=c("Non-contrast", "Contrast")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.text = element_text(size=16),
        strip.text = element_text(size=16),
        axis.text = element_text(size = 16),
        text = element_text(size=16))+
  guides(fill = guide_legend(ncol = 2, byrow=F))+
  scale_fill_brewer(palette="Greys",
                    breaks=c( "Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))

mylegend<-g_legend(ddm_boot_plot)

grob_name <- names(mylegend$grobs)[1]

#manually fix the legend
#move non-decision down
#key
mylegend$grobs[grob_name][[1]]$layout[11,c(1:4)] <- c(4,8,4,8)
mylegend$grobs[grob_name][[1]]$layout[12,c(1:4)] <- c(4,8,4,8)
#text
mylegend$grobs[grob_name][[1]]$layout[17,c(1:4)] <- c(4,10,4,10)
#move threshold down
#key
mylegend$grobs[grob_name][[1]]$layout[9,c(1:4)] <- c(3,8,3,8)
mylegend$grobs[grob_name][[1]]$layout[10,c(1:4)] <- c(3,8,3,8)
#text
mylegend$grobs[grob_name][[1]]$layout[16,c(1:4)] <- c(3,10,3,10)
#move drift rate right and up
#key
mylegend$grobs[grob_name][[1]]$layout[7,c(1:4)] <- c(2,8,2,8)
mylegend$grobs[grob_name][[1]]$layout[8,c(1:4)] <- c(2,8,2,8)
#text
mylegend$grobs[grob_name][[1]]$layout[15,c(1:4)] <- c(2,10,2,10)

mycaption = textGrob(label = str_wrap("FIGURE 7: Average bootstrapped reliability estimates per measure comparing raw measures and model parameters as well as contrast and non-contrast measures for task measures.", width = 130), gp = gpar(fontfamily="Times", lineheight = 2, fontsize = 18), hjust = 0, vjust = 0.5, x = unit(0, "npc"))

ddm_boot_legend = arrangeGrob(ddm_boot_plot +theme(legend.position="none"),
             mylegend, mycaption, nrow=3, heights=c(10, 1, 1))

ggsave('Bootstrap_DDM_Comp_Legend.tiff', plot = ddm_boot_legend, device = "tiff", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 14, height = 10, units = "in", limitsize = FALSE, dpi=300)
```

@@

```{r}
tmp2 = measure_labels %>%
  mutate(dv = as.character(dv),
         contrast = ifelse(overall_difference == "difference", "contrast", "non-contrast")) %>%
  filter(ddm_task == 1,
         rt_acc != 'other') %>%
  drop_na() %>%
  left_join(rel_df[,c("dv", "icc")], by = 'dv')

ddm_point_plot = tmp2 %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_wrap(~factor(contrast, levels=c("non-contrast", "contrast"), labels=c("Non-contrast", "Contrast")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.text = element_text(size=16),
        strip.text = element_text(size=16),
        axis.text = element_text(size = 16),
        text = element_text(size=16))+
  guides(fill = guide_legend(ncol = 2))+
  scale_fill_brewer(palette="Greys",
                    breaks=c( "Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))+
  ylim(-0.4, 1)

mylegend<-g_legend(ddm_point_plot)

grob_name <- names(mylegend$grobs)[1]

#manually fix the legend
#move non-decision down
#key
mylegend$grobs[grob_name][[1]]$layout[11,c(1:4)] <- c(4,8,4,8)
mylegend$grobs[grob_name][[1]]$layout[12,c(1:4)] <- c(4,8,4,8)
#text
mylegend$grobs[grob_name][[1]]$layout[17,c(1:4)] <- c(4,10,4,10)
#move threshold down
#key
mylegend$grobs[grob_name][[1]]$layout[9,c(1:4)] <- c(3,8,3,8)
mylegend$grobs[grob_name][[1]]$layout[10,c(1:4)] <- c(3,8,3,8)
#text
mylegend$grobs[grob_name][[1]]$layout[16,c(1:4)] <- c(3,10,3,10)
#move drift rate right and up
#key
mylegend$grobs[grob_name][[1]]$layout[7,c(1:4)] <- c(2,8,2,8)
mylegend$grobs[grob_name][[1]]$layout[8,c(1:4)] <- c(2,8,2,8)
#text
mylegend$grobs[grob_name][[1]]$layout[15,c(1:4)] <- c(2,10,2,10)

ddm_point_legend = arrangeGrob(ddm_point_plot +theme(legend.position="none"),
             mylegend, nrow=2, heights=c(10, 1))

ggsave('PointEst_DDM_Comp.jpg', plot=ddm_point_legend, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 15, height = 7, units = "in", limitsize = FALSE)
```

>>>>

@@

```{r warning=FALSE, message=FALSE}
trial_num_rel_df %>%
  gather(key, value, -breaks) %>%
  filter(key %in% c("avg_rt_icc", "learning_to_learn_icc", "nonperseverative_errors_icc")) %>%
  ggplot(aes((breaks+1)*10, value, shape=key))+
  geom_point()+
  geom_line(alpha = 0.5)+
  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
                             plot.caption = element_text(family = "Times", lineheight = 2, hjust = 0)) +
  scale_shape_manual(values = c(0:9),
                     breaks = c("avg_rt_icc","learning_to_learn_icc", "nonperseverative_errors_icc"),
                     labels = c("Average Response Time", "Learning to Learn",  "Nonperseverative Errors")) +
  labs(caption = str_wrap("FIGURE 6: Change in point estimates of ICC for three dependent measures selected from the Shift task using increasing numbers of trials to estimate them. These measures show the different types of relationships reliability estimates have based on the trial numbers used to estimate them.", width = 180))
```

@@

```{r}
summary(lmerTest::lmer(icc ~ contrast + (1|dv) ,tmp))
# summary(MCMCglmm(icc ~ contrast, random = ~ dv, data=tmp, verbose=FALSE))
```

@@

```{r echo=FALSE}
rm(icc_by_rawfit_con_model, icc_by_rawfit_noncon_model)
```

```{r echo=FALSE, out.width='100%'}
fig_name = 'Bootstrap_DDM_Comp_Legend.jpeg'

@@

```{r echo=FALSE, out.width='100%'}
fig_name = 'PointEst_DDM_Comp.jpeg'
